A comparison of two second order traffic flow models

### 2015-03-13 FirstDraftMaterials/Draft.tex
Reordered example section

\begin{table}[t]
\caption{Initial values used in examples 1 and 2.}
\begin{center}
\begin{tabular}{| c | c c  c c|}
\hline
& $v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
Example 1 & 0.2 & .03 & 0.3 & 0.4 \\
Example 2 & 0 & 0 & 0.3 & 0.4\\
\hline
\end{tabular}
\end{center}
 \label{table:1}
\end{table}

@@

In both examples the density and velocity are greater in the right state than in the left state.  This corresponds to the situation considered by Aw and Rascle that motivated the use of the convective derivative.  In the first example, we see that the AR model predicts that the density of the middle state is less than both left or right states, but that the velocity increases steadily from left state to the middle state and then remains constant while the density changes due to the contact discontinuity.  This is what we would expect, as drivers spread out as they accelerate to catch up with the cars ahead.  On the other hand, the PW model predicts that the middle state will have a greater density than the left state but a smaller velocity.  This is opposite of what we would expect.

@@

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model. The transition from $q_l$ to $q_r$ is first a shock and then a contact discontinuity.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example1.jpg}
   }
    \subfigure[Solution from the PW model.  The transition from $q_l$ to $q_r$ is first a shock and then a rarefaction wave. ]{
  \includegraphics[width=70mm]{../MatlabCode/Images/PW_example1.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 from the AR and PW models. The middle state is denoted by $q_m$.}
  \label{fig:example1}
\end{figure}

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model. The transition from $q_l$ to $q_r$ is a contact discontinuity,  shown in blue, there is no middle state.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example2.jpg}
   }
 \subfigure[Solution from the PW model. The transition from $q_l$ to $q_r$ is a rarefaction wave, shown in dark green, there is no middle state.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/PW_example2.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 from the AR and PW models.}
  \label{fig:example2}
\end{figure}

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../ClawpackCode/AR/ARexample1.png}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../ClawpackCode/PW/PWexample1.png}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 computed in Clawpack.}
  \label{fig:example2}
\end{figure}

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../ClawpackCode/AR/ARexample2.png}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../ClawpackCode/PW/PWexample2.png}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 computed in Clawpack.}
  \label{fig:example2}
\end{figure}

>>>>

@@

\vspace{-2ex}
\begin{table}[H]
\caption{Initial values used in examples 1 and 2.}
\begin{center}
\begin{tabular}{| c | c c  c c|}
\hline
& $v_l$ & $\rho_l $ & $v_r$ & $\rho_r $\\
\hline
Example 1 & 0.2 & .03 & 0.3 & 0.4 \\
Example 2 & 0 & 0 & 0.3 & 0.4\\
\hline
\end{tabular}
\end{center}
 \label{table:1}
\end{table}

\vspace{-4ex}
In both examples the density and velocity are greater in the right state than in the left state.  This corresponds to the situation considered by Aw and Rascle that motivated the use of the convective derivative.  In the first example, we see that the AR model predicts that the density of the middle state is less than both left or right states, but that the velocity increases steadily from left state to the middle state and then remains constant while the density changes due to the contact discontinuity.  This is what we would expect, as drivers spread out as they accelerate to catch up with the cars ahead.  On the other hand, the PW model predicts that the middle state will have a greater density than the left state but a smaller velocity.  This is opposite of what we would expect.

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model. The transition from $q_l$ to $q_r$ is first a shock and then a contact discontinuity.]{
  \includegraphics[width=60mm]{../MatlabCode/Images/AR_example1.jpg}
   }
    \subfigure[Solution from the PW model.  The transition from $q_l$ to $q_r$ is first a shock and then a rarefaction wave. ]{
  \includegraphics[width=60mm]{../MatlabCode/Images/PW_example1.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 from the AR and PW models. The middle state is denoted by $q_m$.}
  \label{fig:example1}
\end{figure}

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=65mm]{../ClawpackCode/AR/ARexample1.png}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=65mm]{../ClawpackCode/PW/PWexample1.png}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 computed in Clawpack.}
  \label{fig:example1_PW}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model. The transition from $q_l$ to $q_r$ is a contact discontinuity,  shown in blue, there is no middle state.]{
  \includegraphics[width=60mm]{../MatlabCode/Images/AR_example2.jpg}
   }
 \subfigure[Solution from the PW model. The transition from $q_l$ to $q_r$ is a rarefaction wave, shown in dark green, there is no middle state.]{
  \includegraphics[width=60mm]{../MatlabCode/Images/PW_example2.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 from the AR and PW models.}
  \label{fig:example2}
\end{figure}

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=65mm]{../ClawpackCode/AR/ARexample2.png}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=65mm]{../ClawpackCode/PW/PWexample2.png}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 computed in Clawpack.}
  \label{fig:example2_PW}
\end{figure}
